---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# arcgis

<!-- badges: start -->
[![R-CMD-check](https://github.com/R-ArcGIS/arcgis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/R-ArcGIS/arcgis/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

**NOTE**: under active development! We'd love to hear from you on how you would like to use locations services R packages. Please [start a discussion](https://github.com/R-ArcGIS/arcgis/discussions) and we'll get back to you there! 

arcgis is a meta-package that loads ArcGIS location services packages. As of this writing, it includes the packages  [`{arcgislayers}`](https://github.com/R-ArcGIS/arcgislayers), and [`{arcgisutils}`](https://github.com/R-ArcGIS/arcgisutils). 

- `arcgislayers` is the workhorse package that interacts with feature services and image servers
- `arcgisutils` is a developer oriented package that is used for crafting requests to be used by other location service packages such as `arcgislayers`

Please refer to [`arcgislayers`](https://r.esri.com/arcgislayers/) package site for examples. 

## Installation

You can install the development version of arcgis from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("R-ArcGIS/arcgis")
```

## Example


```{r example}
library(arcgis)

health_rankings_url <- "https://services.arcgis.com/P3ePLMYs2RVChkJx/arcgis/rest/services/2022_County_Health_Rankings/FeatureServer"

arc_open(health_rankings_url)
```
